Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-11 astronum_2017/astronum-amrex.tex
add comment about domain volume

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{titan_edison_maestro_scaling}
\begin{minipage}[b]{0.48\linewidth}
\caption{\label{fig:maestro_scaling} \maestro\ strong scaling on NERSC
  edison and OLCF titan for a 3-d XRB problem.  Two different problem
  sizes are shown.\vspace{2em}}
\end{minipage}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{sedov_scaling}
\includegraphics[width=0.48\linewidth]{wdmerger_scaling}
\caption{\label{fig:castro-scaling} (left) \castro\ strong scaling on OLCF titan
for a pure hydro (Sedov) problem; (right) \castro\ strong scaling
on OLCF titan for a hydro + Poisson gravity (wdmerger) problem.}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{summitdev_scaling}
\includegraphics[width=0.48\linewidth]{cori_scaling}
\caption{\label{fig:knl-gpu-scaling} \castro\ scaling on new architectures.}
\end{figure}

Figure~\ref{fig:scaling} shows strong scaling for \maestro\ on the 3-d
XRB problem.  We see that the code scales well to $\mathcal{O}(10^4)$
processors.  The main limitation to the scaling at the moment are the
multigrid solves used to enforce the projection (in particular the
nodal solver).  \maestro\ also does not yet take advantage of the
tiling capabilities offered in \amrex.  These will be addressed in the
future as we port \maestro\ to the C++ \amrex\ codebase to take advantage
of ongoing development.

Figure~\ref{fig:castro-scaling}

@@

Figure~\ref{fig:knl-gpu-scaling} shows the performance of \starlord\ on the
summitdev platform at OLCF\footnote{summitdev consists of 2 IBM Power8
  processors and 4 Nvidia Pascal GPUs per node.}.  The highest GPU
count (128) corresponds to 32 nodes on summitdev.  We see a nearly
linear speedup with the number of GPUs, indicating good weak scaling
on this machine.  Efforts are underway to complete the port of the GPU
developments into \castro.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{titan_edison_maestro_scaling}
\begin{minipage}[b]{0.48\linewidth}
\caption{\label{fig:maestro_scaling} \maestro\ strong scaling on NERSC
  edison and OLCF titan for a 3-d XRB problem.  Two different problem
  sizes are shown.  We see excellent strong scaling to high core counts
  for this problem.\vspace{2em}}
\end{minipage}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{sedov_scaling}
\includegraphics[width=0.48\linewidth]{wdmerger_scaling}
\caption{\label{fig:castro-scaling} (left) \castro\ strong scaling on
  OLCF titan for a pure hydro (Sedov w/ real EOS) problem.  The
  different colors represent different base resolutions.  We see
  excellent strong and weak scaling for the single level runs.  For
  the $1024^3$ run, we also ran with one $2\times$ jump level of
  refinment (triangles) and see good strong scaling.  The variability
  (shown by the error bars) at high core counts shows we are becoming
  work-starved. (right) \castro\ strong scaling on OLCF titan for a
  hydro + Poisson gravity (wdmerger) problem.  This problem uses a
  multipole solver to determine Dirichlet boundary conditions
  representing an isolated mass distribution, and then geometric
  multigrid to solve for the potential in the interior.  Two coarse
  grid sizes are shown, and demonstrate great strong scaling.  We also
  look at a single level of refinement (a $4\times$ jump) on top of
  this coarse grid.}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{summitdev_scaling}
\includegraphics[width=0.48\linewidth]{cori_scaling}
\caption{\label{fig:knl-gpu-scaling} \castro\ scaling on new
  architectures.  The left figure shows the \castro\ GPU proxy app
  (\starlord) on OLCF summitdev.  We see good scaling behavior to 64
  GPUs in this test of a pure hydro problem (Sedov w/ real EOS).  On the
right, we explore performance on NERSC Cori (and Intel KNL platform).}
\end{figure}

Figure~\ref{fig:scaling} shows strong scaling for \maestro\ on the 3-d
XRB problem.  We ran on both OLCF titan and NERSC edison.  We see that
the code scales well to $\mathcal{O}(10^4)$ processors.  The main
limitation to the scaling at the moment are the multigrid solves used
to enforce the projection (in particular the nodal solver).
\maestro\ also does not yet take advantage of the tiling capabilities
offered in \amrex.  These will be addressed in the future as we port
\maestro\ to the C++ \amrex\ codebase to take advantage of ongoing
development.

Figure~\ref{fig:castro-scaling} shows scaling behavior for a pure
hydro + real EOS problem and a hydro / real EOS, + self-gravity
problem.  All tests were run on OLCF titan.  The AMD processors in
titan can be used in a 8 or 16 cores / node configuration.  For all
these runs, we ran in the 16 cores / node mode.  All runs also used
the PGI 17.7 compilers.  We see excellent scaling behavior for the
pure hydro problem.  For the self-gravity problem, we scale well with
a uniform grid, but with a $4\times$ jump for the AMR level on top of
this, we do worse at higher core counts.  This is a challenging
problem, as only 3\% of the domain volume is refined.  For a given
core count, there are a number of different combinations of MPI ranks
and OpenMP threads we can use.  In general, with multilevel problems,
we found the best performance with fewer MPI ranks and more OpenMP
threads.

@@

Figure~\ref{fig:knl-gpu-scaling} shows the performance of
\starlord\ on the summitdev platform at OLCF\footnote{summitdev
  consists of 2 IBM Power8 processors and 4 Nvidia Pascal GPUs per
  node.}.  The highest GPU count (128) corresponds to 32 nodes on
summitdev.  We see a nearly linear speedup with the number of GPUs,
indicating good weak scaling on this machine.  Efforts are underway to
complete the port of the GPU developments into \castro.  This figure
also shows our performance on the Intel KNL manycore processors (using
NERSC Cori).  This is for the same problem as the self-gravity test on
titan. \MarginPar{need more info: base grid?}  The KNL chips in Cori
have 68 cores than can be run with 1, 2, or 4 hardware threads each.
For all these runs, we ran with 4 threads / core (effectively 272
threads / chip).
